Contextual recruitment of selective attention can be updated via changes in task-relevance

### 2019-07-17 manuscript_pretty.Rmd
revision in progress

## Participants
All participants were recruited from Amazon Mechanical Turk (AMT) and compensated $2.00 for participating. The amount compensated was calculated by estimating the maximum amount of time required to complete each experiment and multiplying by $6.00 per hour. For each experiment the number of HITs (Human intelligence tasks, an Amazon term for a work-unit) refers to the number of participants who initiated the study. Participants were included in the study if they completed all trials. We posted 150 HITs and 144 participants completed all trials.

@@

## Design 
Experiment 1 used a 2x2x3 mixed design with task-relevant context (0% and 100%) and unbiased-item congruency (congruent and incongruent) as within-subject factors, and context-type (object, social, and social/non-repeating) as the between-subjects factor.
All three conditions were constructed using the same general method. The experiment was divided into two phases. Each phase consisted of 144 flanker trials (48 trials per context), and 13 count response trials for a total of 314 trials. On the count response trials, participants indicated how many trials they had counted until that point. The count response trials occurred once for every 12 flanker trials and was randomly inserted between trial 6 and 12 of each 12-trial block. Each phase ended with one additional count response trial.

@@

## Data Analysis 
All analyses in this and the following experiments were performed in R [@r_software_2019] using a variety of R packages (). In particular, we used the afex and car packages [@r_afex_2019; @r_car_2019] to perform all the Null Hypothesis Significance Tests, the BayesFactor package to perform Bayesian analyses [@r_bayesfactor_2018], and the conflictPower package to perform the simulation-based sensitivity and power analyses [@r_conflictPower_2019]. All data and scripts can be found

We supplemented each Null Hypothesis Significance Test with a Bayes Factor analysis (Rouder, Speckman.. 2009). Using conventional frequentist testing it is not possible to quantify the evidence for a null effect. Bayes Factors, however, quantify the degree to which the observed data are compatible with either the alternative or null hypothesis (Dienes, 2014; Rouder et al., 2014). All Bayesian analyses were performed using the R package BayesFactor and Bayes Factors (BFs) were calculated using its default settings (Morey and Rouder, 2014). Following the guidelines recommended by Rouder et al. (2009)

@@

The primary question of interest was whether the task-relevance of context features associated with different levels of conflict would influence the size of the congruency effect for frequency unbiased items (see Table 1). To that end, congruency effects (incongruent minus congruent performance) from frequency unbiased trials were submitted to a mixed analysis of variance (ANOVA) with task-relevant context (0% and 100% PC) and context-type (object, social, and social/non-repeating) as the between-subjects factor.

The results of the RT analysis revealed the critical, two-way interaction between task-relevant context and unbiased-item congruency to be significant, `r RT_ANOVA$Task_Relevant_Context`, demonstrating smaller congruency effects when the context dimension associated with high conflict was made task-relevant. Additionally, the three-way interaction between the task-relevant context, unbiased-item congruency, and context-type was non-significant, `r RT_ANOVA$Condition_Task_Relevant_Context`, showing no evidence for differences between the CSPC effects across context-type manipulations.

Similarly, the corresponding error analysis also resulted in a significant two-way interaction between the task-relevant context and unbiased-item congruency, `r ACC_ANOVA$Task_Relevant_Context`, and a non-significant three-way interaction between task-relevant context, unbiased-item congruency, and context-type, `r ACC_ANOVA$Condition_Task_Relevant_Context`. Therefore, the congruency effects in error rates were also smaller when the context dimension associated with high conflict was made task-relevant, corroborating the results of the reaction time analysis.

## Exploratory Analyses: Order Effects

```{r figure2b, echo=FALSE,fig.width=6.875, fig.height= 4, fig.cap='(ref:figure2)'}
#, out.width="\\textwidth", fig.env="figure*"
#print figure 2
#source: data-analysis/analysis.R
figure2B
```

Previous work has shown that the effects of shifting between list-wide proportion congruent phases is asymmetrical. Abrahamse et al.... found that...  In our study, we were primarily interested in whether (a) participants could use context cues despite the presence of competing, contradictory cues, and (b) whether participants could switch from one context cue to another. We therefore randomized the order across participants to control for the effects of order. However, given that we did find systematic shifts in the CSPC effect for unbiased items, we can also ask whether the shift between phases was symmetrical in our study.

To address this question, we collapsed over context-type and categorized participants according to the order of the counting task: 100% congruent to 0% congruent (100%-0%) or 0% congruent to 100% congruent (0%-100%). We again removed participants with error rates greater than 25% and adopted the same outlier removal procedure as described above. We submitted mean correct RTs for frequency unbiased items to a 2x2x2 mixed ANOVA with task-relevant context (0% and 100% PC) and unbiased-item congruency (congruent and incongruent) as within-subject factors, and phase order (100%-0% and 0%-100%) as the between-subjects factor.

Consistent with the original analysis, two-way interaction between task-relevant context and congruency remained significant,`r E1_Order_A$Congruency_Task_Relevant_Context`. However, the three-way interaction was non-significant, `r E1_Order_A$Order_Congruency_Task_Relevant_Context`. Therefor, we did not find statistical support for a list-shift asymmetry. Additionally, the asymmetry we do see in this sample is in the opposite direction than would be predicted given the prior results ().

We also conducted a more severe test of the list-shift hypothesis. Abrahamse et al.'s interpretation of the list shift effect was that participants had to learn to adjust to the new cues. Therefore, we might expect that any asymmetry would be exaggerated near the point of transition. We repeated the above analysis but restricted it to the 24 trials immediately before the transition and 24 trials immediately after the transition.

Again, the three-way interaction was non-significant, `r E1_Order_B$Order_Congruency_Task_Relevant_Context`. Interestingly, the two-way interaction between congruency and task-relevant context is also still significant, `r E1_Order_B$Congruency_Task_Relevant_Context`. This result supports the notion there was no asymmetry and that the shift in context-dependent effects occur almost immediately after the transition.

@@

>>>>

## Participants
All participants were recruited from Amazon Mechanical Turk (AMT) and compensated \$2.00 for participating. The amount compensated was calculated by estimating the maximum amount of time required to complete each experiment and multiplying by \$6.00 per hour. For each experiment the number of HITs (Human intelligence tasks, an Amazon term for a work-unit) refers to the number of participants who initiated the study. Participants were included in the study if they completed all trials. We posted 150 HITs and 144 participants completed all trials.

@@

## Design 
Experiment 1 used a 2x2x3 mixed design with task-relevant context (0% and 100%) and unbiased-item congruency (congruent and incongruent) as within-subject factors, and context-type (object, social, and social/non-repeating) as the between-subjects factor.

All three conditions were constructed using the same general method. The experiment was divided into two phases. Each phase consisted of 144 flanker trials (48 trials per context), and 13 count response trials for a total of 314 trials. On the count response trials, participants indicated how many trials they had counted until that point. The count response trials occurred once for every 12 flanker trials and was randomly inserted between trial 6 and 12 of each 12-trial block. Each phase ended with one additional count response trial.

@@

## Data Analysis 
All analyses in this and the following experiments were performed in R [@r_software_2019] using a variety of R packages and resources [@r_wickham_ggplot2_2016; @r_wickham_dplyr_2019; @r_papaja_2018; @r_cowplot_2019]. Of particular note: we used the afex and car packages to perform all the Null Hypothesis Significance Tests [@r_afex_2019; @r_car_2019], the BayesFactor package to perform Bayesian analyses [@r_bayesfactor_2018], and the conflictPower package to perform the simulation-based sensitivity and power analyses [@r_conflictPower_2019]. All data and scripts can be found on the Open Science Framework (https://osf.io/ztcyb/).

We supplemented each Null Hypothesis Significance Test with a Bayes Factor analysis [@rouder_bayesian_2009]. Using conventional frequentist testing it is not possible to quantify the evidence for a null effect. A Bayes Factor, however, is a continuous measure of the relative strength of evidence and can quantify the degree to which the data are compatible with the null over the alternative hypothesis [@dienes_using_2014; @rouder_bayesian_2009]. All Bayesian analyses were performed using the R package BayesFactor and Bayes Factors ($\mathrm{BFs}$) were calculated using its default settings [@r_bayesfactor_2018]. $\mathrm{BF}_{\textrm{10}}$ indicates evidence in favor of the alternative hypothesis whereas $\mathrm{BF}_{\textrm{01}}$ indicates evidence in favor of the null hypothesis. To simplify the interpretation, we report the Bayes Factor in the direction the data supports (e.g.,  $\mathrm{BF}_{\textrm{01}}$ when there is more evidence in favor of the null over alternative hypothesis). As per previous recommendations, we refer to a $\mathrm{BF > 3}$ as "moderate" and $\mathrm{BF > 10}$ as "strong" evidence [@jeffreys1961theory; @rouder_bayesian_2009].

@@

The primary question of interest was whether the task-relevance of context features associated with different levels of conflict would influence the size of the congruency effect for frequency unbiased items (see Table 1). To that end, congruency effects (incongruent minus congruent performance) from frequency unbiased trials were submitted to a mixed analysis of variance (ANOVA) with task-relevant context (0\% and 100\% PC) as the within-subjects factor and context-type (object, social, and social/non-repeating) as the between-subjects factor. We supplement each Null Hypothesis Significance Test with a corresponding Bayesian analysis.

The results of the reaction time analysis revealed a significant effect of the task-relevant context, `r RT_ANOVA$Task_Relevant_Context`, with moderate evidence in favor of the alternative, `r pRT_BF[[2]]`. Specifically, we found smaller congruency effects when the context dimension associated with high conflict was made task-relevant as compared to when the low conflict dimension was made task-relevant. The main effect of context-type, however, was non-significant, `r RT_ANOVA$Condition`, with moderate evidence in favor of the null hypothesis, `r pRT_BF[[1]]`. The two-way interaction between the task-relevant context and context-type was also non-significant, `r RT_ANOVA$Condition_Task_Relevant_Context`, with moderate evidence in favor of the null hypothesis, `r pRT_BF[[4]]`. Finally, the preferred model containing only the task-relevant context was preferred over the model containing the both factors and the interaction by a factor of `r BF_contrast`. Therefore, congruency effects did not vary across context-types and, more importantly, the effect of task-relevance did not vary across context-types.

Similarly, the corresponding error analysis also resulted a significant effect of the task-relevant context, `r ACC_ANOVA$Task_Relevant_Context`, with moderate evidence in favor of the alternative evidence `r pACC_BF[[2]]`; A non-significant effect of context-type, `r ACC_ANOVA$Condition`, with moderate evidence for the null hypothesis, `r pACC_BF[[1]]`; And a non-significant interaction between task-relevant context and context-type,`r ACC_ANOVA$Condition_Task_Relevant_Context`, with strong evidence in favor of the null hypothesis,`r pACC_BF[[4]]`. Therefore, the congruency effects in error rates were also smaller when the context dimension associated with high conflict was made task-relevant and effects did not vary across context-type, corroborating the results of the reaction time analysis.

## Exploratory analyses: Order effects

```{r figure2b, echo=FALSE,fig.width=6.875, fig.height= 4, fig.cap='(ref:figure2b)'}
#, out.width="\\textwidth", fig.env="figure*"
#print figure 2
#source: data-analysis/analysis.R
figure2B
```

(ref:figure2b) Results from Experiment 1 showing congruency effects (incongruent - congruent) for frequency unbiased items in reaction times as a function of the task-relevant context (100% proportion congruent versus 0% proportion congruent) and phase order (100% to 0% PC versus 0% to 100% PC). Figure A shows a summary of the data containing all trials, whereas Figure B shows a summary of the data restricted to the 24 trials immediately before and 24 trials immediately after the transition. In both cases, the interaction was non-significant ($p > .05$) and Bayesian analyses showed moderate evidence in favor of the null hypothesis ($\mathrm{BF}_{\textrm{01}} > 3$).

Previous work has shown that shifting between list-wide proportion congruent phases produced asymmetrical effects. Specifically, @abrahamse_attention_2013 found that shifting from a mostly-congruent to mostly-incongruent list produced a large change in the size of the congruency effect, whereas shifting from a mostly-incongruent to mostly-congruent list produced a relatively small change in congruency effects. The authors suggested that the assymetry is caused by a learned attentional modulation in the mostly-incongruent block carrying over into the mostly-congruent block. In our study, we were primarily interested in whether (a) participants could use context cues despite the presence of competing, contradictory cues, and (b) whether participants could switch from the use of one context cue to another. We therefore randomized the order across participants to control for the effects of order. However, given that we did find systematic shifts in the CSPC effect for unbiased items, we can also ask whether the shift between phases was asymmetrical.

To address this question, we collapsed over context-type and categorized participants according to the order of the counting task: 100% congruent to 0% congruent (100%-0%) or 0% congruent to 100% congruent (0%-100%). We again removed participants with error rates greater than 25% and adopted the same outlier removal procedure as described above. We submitted congruency effects for frequency unbiased items to a 2x2 mixed ANOVA with task-relevant context (0% and 100% PC) as within-subject factors and phase order (100%-0% and 0%-100%) as the between-subjects factor, and supplemented each test with a corresponding Bayesian analysis.

Consistent with the original analysis, the effect of task-relevant context was significant,`r E1_Order_A$Task_Relevant_Context`, with moderate evidence in favor of the alternative, `r pE1_Order_A_BF[[2]]`. However, the two-way interaction between task-relevant context and phase order was non-significant, `r E1_Order_A$Order_Task_Relevant_Context`, with moderate evidence in favor of the null hypothesis, `r pE1_Order_A_BF[[4]]`. Therefore, we did not find statistical support for a list-shift asymmetry. Additionally, the (non-significant) asymmetrical effects we do see in this sample is in the opposite direction than would be predicted given the prior research [e.g., @abrahamse_attention_2013].

We conducted an additional, more severe test, of the list-shift hypothesis. Given that the asymmetry is interpreted as resulting from a carry-over of learned attentional modulation across phases, we might expect that any asymmetry would be exaggerated near the point of transition. We therefore repeated the above analysis but restricted it to the 24 trials immediately before the transition and 24 trials immediately after the transition.

Again, the interaction between task-relevant context and phase order was non-significant, `r E1_Order_B$Order_Task_Relevant_Context`, with moderate to strong evidence in favor of the null `r pE1_Order_B_BF[[4]]`. Interestingly, the main effect of task-relevant context was still significant, `r E1_Order_B$Task_Relevant_Context`, with moderate evidence in favor of the alternative, `r pE1_Order_B_BF[[2]]`. This result supports the conclusion that there was no asymmetry. Additionally, the the shift in context-dependent effects appears to have taken place almost immediately after the transition.

@@

## Participants
All participants were recruited from Amazon Mechanical Turk (AMT) and compensated \$2.00 for participating. The amount compensated was calculated by estimating the maximum amount of time required to complete each experiment and multiplying by \$6.00 per hour. For each experiment the number of HITs (Human intelligence tasks, an Amazon term for a work-unit) refers to the number of participants who initiated the study. Participants were included in the study if they completed all trials. We posted 50 HITs and 50 participants completed all trials.

### 2019-07-17 manuscript_pretty.tex
revision in progress

Experiment 1 used a 2x2x3 mixed design with task-relevant context (0\% and 100\%) and unbiased-item congruency (congruent and incongruent) as within-subject factors, and context-type (object, social, and social/non-repeating) as the between-subjects factor.
All three conditions were constructed using the same general method. The experiment was divided into two phases. Each phase consisted of 144 flanker trials (48 trials per context), and 13 count response trials for a total of 314 trials. On the count response trials, participants indicated how many trials they had counted until that point. The count response trials occurred once for every 12 flanker trials and was randomly inserted between trial 6 and 12 of each 12-trial block. Each phase ended with one additional count response trial.

@@

@@

The primary question of interest was whether the task-relevance of context features associated with different levels of conflict would influence the size of the congruency effect for frequency unbiased items (see Table 1). To that end, mean correct RTs and mean error rates from frequency unbiased trials were submitted to a mixed analysis of variance (ANOVA) with task-relevant context (0\% and 100\% PC) and unbiased-item congruency (congruent and incongruent) as within-subject factors, and context-type (object, social, and social/non-repeating) as the between-subjects factor.

The results of the RT analysis revealed the critical, two-way interaction between task-relevant context and unbiased-item congruency to be significant, \(F(1, 128) = 8.30\), \(\mathit{MSE} = 1,608.54\), \(p = .005\), \(\hat{\eta}^2_p = .061\), demonstrating smaller congruency effects when the context dimension associated with high conflict was made task-relevant. Additionally, the three-way interaction between the task-relevant context, unbiased-item congruency, and context-type was non-significant, \(F(2, 128) = 0.00\), \(\mathit{MSE} = 1,608.54\), \(p = .996\), \(\hat{\eta}^2_p = .000\), showing no evidence for differences between the CSPC effects across context-type manipulations.

Similarly, the corresponding error analysis also resulted in a significant two-way interaction between the task-relevant context and unbiased-item congruency, \(F(1, 128) = 6.72\), \(\mathit{MSE} = 13.93\), \(p = .011\), \(\hat{\eta}^2_p = .050\), and a non-significant three-way interaction between task-relevant context, unbiased-item congruency, and context-type, \(F(2, 128) = 0.92\), \(\mathit{MSE} = 13.93\), \(p = .400\), \(\hat{\eta}^2_p = .014\). Therefore, the congruency effects in error rates were also smaller when the context dimension associated with high conflict was made task-relevant, corroborating the results of the reaction time analysis.

\hypertarget{exploratory-analyses-order-effects}{%
\subsection{Exploratory Analyses: Order Effects}\label{exploratory-analyses-order-effects}}

\begin{figure}
\centering
\includegraphics{manuscript_pretty_files/figure-latex/figure2b-1.pdf}
\caption{\label{fig:figure2b}Results from Experiment 1 showing congruency effects (incongruent - congruent) for frequency unbiased items in reaction times (left) and error rates (right) as a function of the task-relevant context (100\% proportion congruent versus 0\% proportion congruent). Task-relevance was manipulated by the secondary feature-counting task.}
\end{figure}

Previous work has shown that the effects of shifting between list-wide proportion congruent phases is asymmetrical. Abrahamse et al\ldots{}. found that\ldots{} In our study, we were primarily interested in whether participants could use context cues despite the presence of competing, contradictory cues, and whether they could switch from one context cue to another. We therefore randomized the order across participants to control for the effects of order. However, given that we did find systematic shifts in the CSPC effect for unbiased items, we can also ask whether the shift between phases was symmetrical in our study.

To address this question, we collapsed over context-type and categorized participants according to the order of the counting task: 100\% congruent to 0\% congruent (100\%-0\%) or 0\% congruent to 100\% congruent (0\%-100\%). We again removed participants with error rates greater than 25\% and adopted the same outlier removal procedure as described above. We submitted mean correct RTs for frequency unbiased items to a 2x2x2 mixed ANOVA with task-relevant context (0\% and 100\% PC) and unbiased-item congruency (congruent and incongruent) as within-subject factors, and phase order (100\%-0\% and 0\%-100\%) as the between-subjects factor.

Consistent with the original analysis, two-way interaction between task-relevant context and congruency remained significant,\(F(1, 129) = 8.92\), \(\mathit{MSE} = 1,627.84\), \(p = .003\), \(\hat{\eta}^2_p = .065\). However, the three-way interaction was non-significant, \(F(1, 129) = 2.56\), \(\mathit{MSE} = 1,627.84\), \(p = .112\), \(\hat{\eta}^2_p = .019\). Therefor, we did not find statistical support for a list-shift asymmetry. Additionally, the asymmetry we do see in this sample is in the opposite direction than would be predicted given the prior results ().

We also conducted a more severe test of the list-shift hypothesis. Abrahamse et al.'s interpretation of the list shift effect was that participants had to learn to adjust to the new cues. Therefore, we might expect that any asymmetry would be exaggerated near the point of transition. We repeated the above analysis but restricted it to the 24 trials immediately before the transition and 24 trials immediately after the transition.

Again, the three-way interaction was non-significant, \(F(1, 129) = 0.02\), \(\mathit{MSE} = 2,866.15\), \(p = .902\), \(\hat{\eta}^2_p = .000\). Interestingly, the two-way interaction between congruency and task-relevant context is also still significant, \(F(1, 129) = 6.65\), \(\mathit{MSE} = 2,866.15\), \(p = .011\), \(\hat{\eta}^2_p = .049\). This result supports the notion there was no asymmetry and that the shift in context-dependent effects occur almost immediately after the transition.

@@

@@

@@

@@

@@

@@

@@

@@

@@

>>>>

Experiment 1 used a 2x2x3 mixed design with task-relevant context (0\% and 100\%) and unbiased-item congruency (congruent and incongruent) as within-subject factors, and context-type (object, social, and social/non-repeating) as the between-subjects factor.

All three conditions were constructed using the same general method. The experiment was divided into two phases. Each phase consisted of 144 flanker trials (48 trials per context), and 13 count response trials for a total of 314 trials. On the count response trials, participants indicated how many trials they had counted until that point. The count response trials occurred once for every 12 flanker trials and was randomly inserted between trial 6 and 12 of each 12-trial block. Each phase ended with one additional count response trial.

@@

\hypertarget{data-analysis}{%
\subsection{Data Analysis}\label{data-analysis}}

All analyses in this and the following experiments were performed in R (R Core Team, 2019) using a variety of R packages and resources (Aust \& Barth, 2018; Wickham, 2016; Wickham, François, Henry, \& Müller, 2019; Wilke, 2019). Of particular note: we used the afex and car packages to perform all the Null Hypothesis Significance Tests (Fox \& Weisberg, 2019; Singmann, Bolker, Westfall, \& Aust, 2019), the BayesFactor package to perform Bayesian analyses (Morey \& Rouder, 2018), and the conflictPower package to perform the simulation-based sensitivity and power analyses (Crump \& Brosowsky, 2019). All data and scripts can be found on the Open Science Framework (\url{https://osf.io/ztcyb/}).

We supplemented each Null Hypothesis Significance Test with a Bayes Factor analysis (Rouder, Speckman, Sun, Morey, \& Iverson, 2009). Using conventional frequentist testing it is not possible to quantify the evidence for a null effect. A Bayes Factor, however, is a continuous measure of the relative strength of evidence and can quantify the degree to which the data are compatible with the null over the alternative hypothesis (Dienes, 2014; Rouder et al., 2009). All Bayesian analyses were performed using the R package BayesFactor and Bayes Factors (\(\mathrm{BFs}\)) were calculated using its default settings (Morey \& Rouder, 2018). \(\mathrm{BF}_{\textrm{10}}\) indicates evidence in favor of the alternative hypothesis whereas \(\mathrm{BF}_{\textrm{01}}\) indicates evidence in favor of the null hypothesis. To simplify the interpretation, we report the Bayes Factor in the direction the data supports (e.g., \(\mathrm{BF}_{\textrm{01}}\) when there is more evidence in favor of the null over alternative hypothesis). As per previous recommendations, we refer to a \(\mathrm{BF > 3}\) as \enquote{moderate} and \(\mathrm{BF > 10}\) as \enquote{strong} evidence (Jeffreys, 1961; Rouder et al., 2009).

@@

The primary question of interest was whether the task-relevance of context features associated with different levels of conflict would influence the size of the congruency effect for frequency unbiased items (see Table 1). To that end, congruency effects (incongruent minus congruent performance) from frequency unbiased trials were submitted to a mixed analysis of variance (ANOVA) with task-relevant context (0\% and 100\% PC) as the within-subjects factor and context-type (object, social, and social/non-repeating) as the between-subjects factor. We supplement each Null Hypothesis Significance Test with a corresponding Bayesian analysis.

The results of the reaction time analysis revealed a significant effect of the task-relevant context, \(F(1, 128) = 8.30\), \(\mathit{MSE} = 3,217.08\), \(p = .005\), \(\hat{\eta}^2_p = .061\), 90\% CI \([0.01\), \(0.14]\), with moderate evidence in favor of the alternative, \(\mathrm{BF}_{\textrm{10}} = 6.87\) \([\pm 1.41\%]\). Specifically, we found smaller congruency effects when the context dimension associated with high conflict was made task-relevant as compared to when the low conflict dimension was made task-relevant. The main effect of context-type, however, was non-significant, \(F(2, 128) = 1.51\), \(\mathit{MSE} = 6,368.18\), \(p = .225\), \(\hat{\eta}^2_p = .023\), 90\% CI \([0\), \(0.07]\), with moderate evidence in favor of the null hypothesis, \(\mathrm{BF}_{\textrm{01}} = 3.96\) \([\pm 1.52\%]\). The two-way interaction between the task-relevant context and context-type was also non-significant, \(F(2, 128) < 0.01\), \(\mathit{MSE} = 3,217.08\), \(p = .996\), \(\hat{\eta}^2_p < .001\), 90\% CI \([0\), \(1]\), with moderate evidence in favor of the null hypothesis, \(\mathrm{BF}_{\textrm{01}} = 7.9\) \([\pm 1.49\%]\). Finally, the preferred model containing only the task-relevant context was preferred over the model containing the both factors and the interaction by a factor of \(54.25\) \([\pm 2.05\%]\). Therefore, congruency effects did not vary across context-types and, more importantly, the effect of task-relevance did not vary across context-types.

Similarly, the corresponding error analysis also resulted a significant effect of the task-relevant context, \(F(1, 128) = 6.72\), \(\mathit{MSE} = 27.87\), \(p = .011\), \(\hat{\eta}^2_p = .050\), 90\% CI \([0.01\), \(0.12]\), with moderate evidence in favor of the alternative evidence \(\mathrm{BF}_{\textrm{10}} = 3.13\) \([\pm 5.2\%]\); A non-significant effect of context-type, \(F(2, 128) = 0.81\), \(\mathit{MSE} = 51.40\), \(p = .449\), \(\hat{\eta}^2_p = .012\), 90\% CI \([0\), \(0.05]\), with moderate evidence for the null hypothesis, \(\mathrm{BF}_{\textrm{01}} = 7.54\) \([\pm 1.22\%]\); And a non-significant interaction between task-relevant context and context-type,\(F(2, 128) = 0.92\), \(\mathit{MSE} = 27.87\), \(p = .400\), \(\hat{\eta}^2_p = .014\), 90\% CI \([0\), \(0.05]\), with strong evidence in favor of the null hypothesis,\(\mathrm{BF}_{\textrm{01}} = 15.04\) \([\pm 2.57\%]\). Therefore, the congruency effects in error rates were also smaller when the context dimension associated with high conflict was made task-relevant and effects did not vary across context-type, corroborating the results of the reaction time analysis.

\hypertarget{exploratory-analyses-order-effects}{%
\subsection{Exploratory analyses: Order effects}\label{exploratory-analyses-order-effects}}

\begin{figure}
\centering
\includegraphics{manuscript_pretty_files/figure-latex/figure2b-1.pdf}
\caption{\label{fig:figure2b}Results from Experiment 1 showing congruency effects (incongruent - congruent) for frequency unbiased items in reaction times as a function of the task-relevant context (100\% proportion congruent versus 0\% proportion congruent) and phase order (100\% to 0\% PC versus 0\% to 100\% PC). Figure A shows a summary of the data containing all trials, whereas Figure B shows a summary of the data restricted to the 24 trials immediately before and 24 trials immediately after the transition. In both cases, the analyses resulted in no significant interaction (\(p > .05\)) and moderate evidence in favor of the null hypothesis (\(\mathrm{BF}_{\textrm{01}} > 3\)).}
\end{figure}

Previous work has shown that shifting between list-wide proportion congruent phases produced asymmetrical effects. Specifically, Abrahamse, Duthoo, Notebaert, and Risko (2013) found that shifting from a mostly-congruent to mostly-incongruent list produced a large change in the size of the congruency effect, whereas shifting from a mostly-incongruent to mostly-congruent list produced a relatively small change in congruency effects. The authors suggested that the assymetry is caused by a learned attentional modulation in the mostly-incongruent block carrying over into the mostly-congruent block. In our study, we were primarily interested in whether (a) participants could use context cues despite the presence of competing, contradictory cues, and (b) whether participants could switch from the use of one context cue to another. We therefore randomized the order across participants to control for the effects of order. However, given that we did find systematic shifts in the CSPC effect for unbiased items, we can also ask whether the shift between phases was asymmetrical.

To address this question, we collapsed over context-type and categorized participants according to the order of the counting task: 100\% congruent to 0\% congruent (100\%-0\%) or 0\% congruent to 100\% congruent (0\%-100\%). We again removed participants with error rates greater than 25\% and adopted the same outlier removal procedure as described above. We submitted congruency effects for frequency unbiased items to a 2x2 mixed ANOVA with task-relevant context (0\% and 100\% PC) as within-subject factors and phase order (100\%-0\% and 0\%-100\%) as the between-subjects factor, and supplemented each test with a corresponding Bayesian analysis.

Consistent with the original analysis, the effect of task-relevant context was significant,\(F(1, 129) = 8.92\), \(\mathit{MSE} = 3,255.69\), \(p = .003\), \(\hat{\eta}^2_p = .065\), 90\% CI \([0.01\), \(0.14]\), with moderate evidence in favor of the alternative, \(\mathrm{BF}_{\textrm{10}} = 8.11\) \([\pm 0.83\%]\). However, the two-way interaction between task-relevant context and phase order was non-significant, \(F(1, 129) = 2.56\), \(\mathit{MSE} = 3,255.69\), \(p = .112\), \(\hat{\eta}^2_p = .019\), 90\% CI \([0\), \(0.07]\), with moderate evidence in favor of the null hypothesis, \(\mathrm{BF}_{\textrm{01}} = 4.92\) \([\pm 2.95\%]\). Therefor, we did not find statistical support for a list-shift asymmetry. Additionally, the (non-significant) asymmetry we do see in this sample is in the opposite direction than would be predicted given the prior research (e.g., Abrahamse et al., 2013).

Additionally, we conducted a more severe test of the list-shift hypothesis. Given that the asymmetry is interpreted as resulting from a carry-over of learned attentional modulation across phases, we might expect that any asymmetry would be exaggerated near the point of transition. We therefore repeated the above analysis but restricted it to the 24 trials immediately before the transition and 24 trials immediately after the transition.

Again, the interaction between task-relevant context and phase order was non-significant, \(F(1, 129) = 0.02\), \(\mathit{MSE} = 5,732.31\), \(p = .902\), \(\hat{\eta}^2_p < .001\), 90\% CI \([0\), \(0.01]\), with moderate to strong evidence in favor of the null \(\mathrm{BF}_{\textrm{01}} = 8.88\) \([\pm 2.88\%]\). Interestingly, the main effect of task-relevant context was still significant, \(F(1, 129) = 6.65\), \(\mathit{MSE} = 5,732.31\), \(p = .011\), \(\hat{\eta}^2_p = .049\), 90\% CI \([0.01\), \(0.12]\), with moderate evidence in favor of the alternative, \(\mathrm{BF}_{\textrm{10}} = 3.22\) \([\pm 2.16\%]\). This result supports the conclusion that there was no asymmetry. Additionally, the the shift in context-dependent effects appears to have taken place almost immediately after the transition.

@@

\leavevmode\hypertarget{ref-abrahamse_attention_2013}{}%
Abrahamse, E. L., Duthoo, W., Notebaert, W., \& Risko, E. F. (2013). Attention modulation by proportion congruency: The asymmetrical list shifting effect. \emph{Journal of Experimental Psychology: Learning, Memory, and Cognition}, \emph{39}, 1552. Retrieved from \url{http://psycnet.apa.org/journals/xlm/39/5/1552/}

@@

\leavevmode\hypertarget{ref-r_papaja_2018}{}%
Aust, F., \& Barth, M. (2018). \emph{papaja: Create APA manuscripts with R Markdown}. Retrieved from \url{https://github.com/crsh/papaja}

@@

\leavevmode\hypertarget{ref-r_conflictPower_2019}{}%
Crump, M. J. C., \& Brosowsky, N. P. (2019). \emph{ConflictPower: Simulation based power analysis for adaptive control designs}. Retrieved from \url{https://github.com/CrumpLab/conflictPower}

@@

\leavevmode\hypertarget{ref-dienes_using_2014}{}%
Dienes, Z. (2014). Using Bayes to get the most out of non-significant results. \emph{Frontiers in Psychology}, \emph{5}. doi:\href{https://doi.org/10.3389/fpsyg.2014.00781}{10.3389/fpsyg.2014.00781}

@@

\leavevmode\hypertarget{ref-r_car_2019}{}%
Fox, J., \& Weisberg, S. (2019). \emph{An R companion to applied regression} (Third.). Thousand Oaks CA: Sage. Retrieved from \url{https://socialsciences.mcmaster.ca/jfox/Books/Companion/}

@@

\leavevmode\hypertarget{ref-jeffreys1961theory}{}%
Jeffreys, H. (1961). \emph{Theory of probability, clarendon}. Oxford: Oxford University Press, Clarendon Press.

@@

\leavevmode\hypertarget{ref-r_bayesfactor_2018}{}%
Morey, R. D., \& Rouder, J. N. (2018). \emph{BayesFactor: Computation of bayes factors for common designs}. Retrieved from \url{https://CRAN.R-project.org/package=BayesFactor}

\leavevmode\hypertarget{ref-r_software_2019}{}%
R Core Team. (2019). \emph{R: A language and environment for statistical computing}. Vienna, Austria: R Foundation for Statistical Computing. Retrieved from \url{https://www.R-project.org/}

\leavevmode\hypertarget{ref-rouder_bayesian_2009}{}%
Rouder, J. N., Speckman, P. L., Sun, D., Morey, R. D., \& Iverson, G. (2009). Bayesian t tests for accepting and rejecting the null hypothesis. \emph{Psychonomic Bulletin \& Review}, \emph{16}, 225--237. doi:\href{https://doi.org/10.3758/PBR.16.2.225}{10.3758/PBR.16.2.225}

@@

\leavevmode\hypertarget{ref-r_afex_2019}{}%
Singmann, H., Bolker, B., Westfall, J., \& Aust, F. (2019). \emph{Afex: Analysis of factorial experiments}. Retrieved from \url{https://CRAN.R-project.org/package=afex}

@@

\leavevmode\hypertarget{ref-r_wickham_ggplot2_2016}{}%
Wickham, H. (2016). \emph{Ggplot2: Elegant graphics for data analysis}. Springer-Verlag New York. Retrieved from \url{https://ggplot2.tidyverse.org}

\leavevmode\hypertarget{ref-r_wickham_dplyr_2019}{}%
Wickham, H., François, R., Henry, L., \& Müller, K. (2019). \emph{Dplyr: A grammar of data manipulation}. Retrieved from \url{https://CRAN.R-project.org/package=dplyr}

\leavevmode\hypertarget{ref-r_cowplot_2019}{}%
Wilke, C. O. (2019). \emph{Cowplot: Streamlined plot theme and plot annotations for 'ggplot2'}. Retrieved from \url{https://CRAN.R-project.org/package=cowplot}
